Prefetching SPARQL query cacher

### 2016-05-18 dissertation/cache-proxy.tex
more on planning

\subsubsection{Analysis and prefetching}

@@

For example, the query planner that can use a local cache and a remote
endpoint, named \pmodule{AtteanX::QueryPlanner::Cache}, extends the
basic query planner of the Attean framework,
\pmodule{Attean::QueryPlanner}, but also composes the following roles:
\pmodule{Attean::API::NaiveJoinPlanner},
\pmodule{Attean::API::SimpleCostPlanner},
\pmodule{AtteanX::API::JoinRotatingPlanner},
\pmodule{AtteanX::Query::AccessPlan::SingleQuadBGP} and
\pmodule{AtteanX::Query::AccessPlan::Cache}.

>>>>

\subsubsection{Analysis and prefetching}\label{sec:analpre}

@@

The query planner is written as completely stand-alone modules, based
on the facilities in the Attean framework, but without accessing
Attean internals. The system has in fact three query planners:
\pmodule{AtteanX::QueryPlanner::Cache},
\pmodule{AtteanX::QueryPlanner::Cache::LDF} and
\pmodule{AtteanX::Query::Cache::Analyzer::QueryPlanner}. Each is an
extension of the previous. The first is written to use a remote
endpoint in combination with a local cache. The second extends this to
also be able to generate and use Triple Pattern Fragments plans. The
final is a query planner for the analyser in Section~\ref{sec:analpre}
that reruns the query planning with all triple patterns in a simulated
cache.

These query planners are a good example of the virtues of traits-based
programming: \pmodule{AtteanX::QueryPlanner::Cache} extends the basic query
planner of the Attean framework, \pmodule{Attean::QueryPlanner}, but
also composes the following roles:
\pmodule{Attean::API::NaiveJoinPlanner},
\pmodule{Attean::API::SimpleCostPlanner},
\pmodule{AtteanX::API::JoinRotatingPlanner},
\pmodule{AtteanX::Query::AccessPlan::SingleQuadBGP} and
\pmodule{AtteanX::Query::AccessPlan::Cache}.

\pmodule{Attean::QueryPlanner} has only minimal functionality,
everything else is provided by the roles. With conventional single
inheritance, one would end up with a rather complex base class. While
multiple inheritance or mix-in could be employed, \cite{traits}
explains why this is an inferior solution.
